Use of significance test logic by scientists in a novel reasoning task

### 2025-03-09 inst/manuscript/manuscript.Rmd
more small changes to prepare for resubmission

Participants also made use of "replications" of the fictional experiments. Figure`~`{=latex}\@ref(fig:sampling)B shows the distribution of the number of experiments sampled as a function of the true effect size. Median numbers of experiments range from 20 when Jinglies and Sparklies were equally fast, down to 9 when the true effect size was $\delta=1$ and thus the effect was relatively easy to detect (`r papaja::apa_print(kt_expt)$statistic`). When the effect size is small and difficult to detect, participants experimented more before deciding.

@@

```{r response-ev, fig.cap="Statistical evidence underlying participants' decisions. The Wilcoxon $p$ value ($x$ axis) used as a rough index of evidential strength in the display. Kernel density estimates for the evidence are shown for three relevant conclusions. Each point at the bottom represents a single participant. Filled circles show correct decisions; hollow circles, incorrect decisions. The two asterisks show sign errors.", out.width=".9\\columnwidth", fig.height=4.8}
MoreyHoekstra2019::fig_response_evidence()
```

>>>>

Participants also made use of "replications" of the fictional experiments. Figure`~`{=latex}\@ref(fig:sampling)B shows the distribution of the number of experiments sampled as a function of the true effect size. Median numbers of experiments range from 20 when Jinglies and Sparklies were equally fast, down to 9 when the true effect size was $\delta=1$ and thus the effect was relatively easy to detect (`r papaja::apa_print(kt_expt)$statistic`). For the small effect sizes, null samples and experimental samples would be expected to appear quite similar; in this case, participants experimented more before deciding.

@@

```{r response-ev, fig.cap="Statistical evidence underlying participants' decisions. The Wilcoxon $p$ value ($x$ axis) used as a rough index of evidential strength in the display. Kernel density estimates for the evidence are shown for three relevant conclusions. Each point at the bottom represents a single participant. Filled circles show correct decisions; hollow circles, incorrect decisions. The two asterisks show sign errors. Some correct decisions with extreme $p$ values are omitted from the left-hand side of the graph for clarity.", out.width=".9\\columnwidth", fig.height=4.8}
MoreyHoekstra2019::fig_response_evidence()
```
